### 2021-04-10 Chapter-5/Chapter-5.tex
Updates from Overleaf

\section{Multiple Leakages Sites}

@@

\begin{itemize}
\item \textbf{Effectiveness:} Can \ctool{} quantify the information leakage with an conservative estimation? If so, what is the loss compared it with the real leakage?
\item \textbf{Performance:} How much overhead can \ctool{} produce?
\item \textbf{Usage:} What is the real usage of \ctool{}? Can \ctool{} handle both Cryptography and Non-cryptography libraries? Can \ctool{} help developers find and fix side-channel leakages?
\end{itemize}

@@

\subsection{Overview}

>>>>

\section{Multiple Leakages Sites}
Real-world software can have various side-channel vulnerabilities. Those vulnerabilities may spread in the whole program. An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}. In order to precisely quantify the
total information leakage, we need to know the relation of those leakage sites.

Suppose one program has two side-channel vulnerabilities A and B, which can leak $L_A$ and $L_B$ bits respectively according to the definition~\ref{chapter5:def}. 
Depending on the relation between A and B, the total leaked information $L_{\mathit{total}}$ will be:

\subsection{Independent Leakages}
If A and B are independent leakages, the total information leakage will be:
$$L_{\mathit{total}} = L_A + L_B $$

\subsection{Dependent Leakages}
If A and B are dependent leakages, the total information leakage will be:
$$\max{\{L_A, L_B\}}  \leq L_{\mathit{total}} < L_A + L_B$$

@@

\begin{itemize}
\item \textbf{Effectiveness:} Can \ctool{} quantify the information leakage with an conservative estimation? If so, what is the loss compared it with the real leakage?
\item \textbf{Performance:} What are overhead costs of \ctool{}?
\item \textbf{Usage:} What is the real usage of \ctool{}? Can \ctool{} handle both Cryptography and Non-cryptography libraries? Can \ctool{} help developers find and fix side-channel leakages?
\end{itemize}

@@

\subsection{Result Overview}
